Hypertension and microbiome

### 2019-06-04 articletwo.Rmd
Maaslin2

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("tags" %in% names(args)) 
        rtags('~/phd/research/articletwo/', recursive = FALSE, pattern = '\\.[RrSs](rw|md)?$',
              ofile = '~/phd/research/articletwo/TAGS', verbose = TRUE, append = FALSE)
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
}
```

@@

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
library(purrr)
```

@@

### EdgeR plot functions

```{r EdgeR functions, code=readLines("aaro/edgeR_plot_functions.R")}
source("aaro/edgeR_plot_functions.R")
```

@@

## Models

@@

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX"),
                                           npermutations = 1000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
                                                          "BL_USE_RX_C03", "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                           npermutations = 1000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

```{r check adonis, eval = FALSE}
ad.min <- adonis(bray.dist.m.species ~ DIASM + BL_AGE + SEX,
             data = meta(pseq.species),
             permutations = 100)

ad.max <- adonis(bray.dist.m.species ~ DIASM + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB +
                     BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09,
             data = meta(pseq.species),
             permutations = 1000)

@@

    maaslin <- list()
    genus.core.bacteria <- pseq.genus.core %>%
        abundances %>%
        rownames %>%
        replace.brackets %>%
        mygrep(".Bacteria$", .)
    maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                    taxa = paste0(genus.core.bacteria, collapse = ","))

>>>>

    if("clean" %in% names(args)) {
        unlink("rds", recursive=TRUE)
        unlink("cache", recursive=TRUE)
    }
    if ("tags" %in% names(args)) 
        rtags('~/phd/research/articletwo/', recursive = FALSE, pattern = '\\.[RrSs](rw|md)?$',
              ofile = '~/phd/research/articletwo/TAGS', verbose = TRUE, append = FALSE)
    if ("loadlast" %in% names(args) )
        load(paste0("session/", sort(list.files("session"), decreasing = TRUE)[1]))
}

#packrat::opts$ignored.packages
```

@@

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(nortest)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(parallel)
library(officer)
library(flextable)
library(xtable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
library(ggpubr)
library(broom)
library(ggfortify)
library(RColorBrewer)
library(gvlma)
library(purrr)
library(Maaslin2)
```

@@

@@

## Variables

```{r variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
```

## MODELS

@@

 ```{r adonis calculation}
 if (!file.exists("rds/adonis.species.rds")) {
     adonis.species = list()
     adonis.species$min <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL.min,
                                           npermutations = 10000)
     adonis.species$max <- calculateadonis(dset = meta(pseq.species),
                                           matrix = bray.dist.m.species,
                                           covariates = var.CL,
                                           npermutations = 10000)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
    } else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

@@

    maaslin.pheno <- t(microbiome::meta(phyloseq::sample_data(pseq.genus))) %>%
        t %>%
        as.data.frame %>%
        select(var.BP, var.CL)

    maaslin.abund <- abundances(pseq.genus.core, transform = "compositional") %>%
        t %>%
        as.data.frame %>%
        select(-contains("virus")) %>%
        select(1:20)

    maaslin <- Maaslin2(maaslin.abund,
             maaslin.pheno,
             paste0("cache/maaslin-", now),
             transform = 'AST',
             fixed_effects = paste0(var.CL, collapse = ","), 
             cores = 10)
